Open source landscape ecology tools

### 2020-10-20 paper/paper.Rmd
adds motif bib and updates the packages table

  \begin{table}
    \begin{tabularx}{0.9\linewidth}{XXXX}
      \caption{Overview of commonly used \textit{R} packages for landscape ecology. Packages are sorted by their major application topic. Only packages especially for spatial data and landscape ecology are included.} \\
      \hline
      Topic & Package & Description & Source \\
      \hline
      \multirow{5}{*}{Spatial data} & \textit{raster} & Methods for raster data & \cite{Hijmans2019} \\
      & \textit{stars} & Methods for spatiotemporal arrays (raster and vector data cubes) & \cite{Pebesma2019} \\
      & \textit{sp} & Methods for mainly vector data & \cite{Pebesma2005,Bivand2013} \\
      & \textit{sf} & Methods for vector data as simple features & \cite{Pebesma2018} \\
      & \textit{landscapetools} & Utility functions for landscape analysis & \cite{Sciaini2018} \\
      \hline
      \multirow{3}{*}{Creating maps} & \textit{tmap} & xxx & xxx \\
      & \textit{mapview} & xxx & xxx \\
      & \textit{leaflet} & xxx & xxx \\
      \hline
      \multirow{2}{*}{Landscape metrics} & \textit{landscapemetrics} & Calculates landscape metrics for categorical land cover maps & \cite{Hesselbarth2019a} \\
      & \textit{belg} & Calculates the Boltzmann entropy of a landscape gradient & \cite{R-belgpaper} \\
      \hline
      \multirow{5}{*}{}Species distribution modeling (SDM) & \textit{dismo} & xxx & xxx \\
      & \textit{sdm} & xxx & xxx \\
      & \textit{ecospat} & xxx & xxx \\
      & \textit{biomod2} & xxx & xxx \\
      & \textit{PresenceAbsence} & xxx & xxx \\
      \hline
      \multirow{3}{*}{Connectivity} & \textit{grainscape} & xxx & \cite{Chubaty2020} \\
      & \textit{gdistance} & xxx & \cite{vanEtten2017} \\
      & \textit{samc} & xxx & \cite{Marx2020} \\
      \hline
      \multirow{3}{*}{Landscape genetics} & \textit{graphs4lg} & xxx & \cite{Savary2020} \\
      & \textit{PopGenReport} & xxx & \cite{Adamack2014,Gruber2015} \\
      & \textit{HierDpart} & xxx & \cite{Qin2019} \\
      \hline
      Neutral Landscape Models (NLM) & \textit{NLMR} & xxx & \cite{Sciaini2018} \\
      \hline
    \end{tabularx}
  \end{table}

>>>>

  \begin{table}
    \begin{tabularx}{0.9\linewidth}{XXXX}
      \caption{Overview of commonly used \textit{R} packages for landscape ecology. Packages are sorted by their major application topic. Only packages focussed on spatial data and landscape ecology are included.} \\
      \hline
      Topic & Package & Description & Source \\
      \hline
      \multirow{5}{*}{Spatial data} & \textit{raster} & Methods for raster data & \cite{Hijmans2019} \\
      & \textit{stars} & Methods for spatiotemporal arrays (raster and vector data cubes) & \cite{Pebesma2019} \\
      & \textit{sp} & Methods for mainly vector data & \cite{Pebesma2005,Bivand2013} \\
      & \textit{sf} & Successor of the sp package. Methods for vector data as simple features & \cite{Pebesma2018} \\
      & \textit{landscapetools} & Utility functions for landscape analysis & \cite{Sciaini2018} \\
      \hline
      \multirow{3}{*}{Creating maps} & \textit{tmap} & Plotting system for static and interactive maps & \cite{Tennekes2018} \\
      & \textit{mapview} & Quick, interactive viewing of spatial data & \cite{R-mapview} \\
      & \textit{leaflet} & Creating interactive web maps & \cite{R-leaflet} \\
      \hline
      \multirow{3}{*}{}Quantifying landscape characteristics & \textit{landscapemetrics} & Calculates landscape metrics for categorical land cover maps & \cite{Hesselbarth2019a} \\
      & \textit{belg} & Calculates the Boltzmann entropy of a landscape gradient & \cite{R-belgpaper} \\
      & \textit{motif} & Enables several type of spatial analysis such as search, change detection, and clustering to be performed on categorical maps  & \cite{R-motif} \\
      \hline
      \multirow{5}{*}{}Species distribution modeling (SDM) & \textit{dismo} & xxx & xxx \\
      & \textit{sdm} & xxx & xxx \\
      & \textit{ecospat} & xxx & xxx \\
      & \textit{biomod2} & xxx & xxx \\
      & \textit{PresenceAbsence} & xxx & xxx \\
      \hline
      \multirow{3}{*}{Connectivity} & \textit{grainscape} & xxx & \cite{Chubaty2020} \\
      & \textit{gdistance} & xxx & \cite{vanEtten2017} \\
      & \textit{samc} & xxx & \cite{Marx2020} \\
      \hline
      \multirow{3}{*}{Landscape genetics} & \textit{graphs4lg} & xxx & \cite{Savary2020} \\
      & \textit{PopGenReport} & xxx & \cite{Adamack2014,Gruber2015} \\
      & \textit{HierDpart} & xxx & \cite{Qin2019} \\
      \hline
      Neutral Landscape Models (NLM) & \textit{NLMR} & xxx & \cite{Sciaini2018} \\
      \hline
    \end{tabularx}
  \end{table}
